Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-13 main.tex
Add proofs

\begin{lemma}\label{lem:shallow}
  Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
\end{lemma}
\juihsuan{For this, we need the introduction rule of $\fff$ in $\FOMLL$
(consider the $\aiD$ rule). But if we add it, we'll need the
$\mathsf{ai}\downarrow$ rule to have Lemma \ref{lem:MLL1->MLS1}}
\lutz{shit. so, we need another way to prove lemma~\ref{lem:MLS1->MLL1}, I'd like to avoid $\fff$-intro.}
\begin{proof}
  This is a straightforward exercise that we leave to the reader.
\end{proof}

@@

Then Theorem~\ref{thm:KS} is an immediate consequence. Let us now
proceed with providing further lemmas that will be needed for the
other results.

@@

\begin{proof}
  \todo{}
\end{proof}

@@

\begin{proof}
  \todo{}\lutz{also check for the need of$\fequ$}
\end{proof}

>>>>

\begin{lemma}\label{lem:shallow}
  Let $\vlinf{\rr}{}{\Scons B}{\Scons A}$ be an inference rule in
  $\FOMLS$. Then the sequent $\sqn{\cneg A,B}$ is provable in $\FOMLL$.
\end{lemma}
\juihsuan{For this, we need the introduction rule of $\fff$ in $\FOMLL$
(consider the $\aiD$ rule). But if we add it, we'll need the
$\mathsf{ai}\downarrow$ rule to have Lemma \ref{lem:MLL1->MLS1}}
\lutz{shit. so, we need another way to prove lemma~\ref{lem:MLS1->MLL1}, I'd like to avoid $\fff$-intro.}
\juihsuan{This lemma holds for all the rules except $\aiD$ (we may need to
mention that $A \fequ B \Rightarrow \ \vdash_{\FOMLL} \dual{B}, A$). The inductive
step for $\aiD$ in the proof of Lemma \ref{lem:MLS1->MLL1} can be solved by
replacing $t$ with $a \vlor \dual{a}$ and the $\ttt$-rule with the $\ax$
 rule followed by the $\vlor$ rule}
\begin{proof}
  This is a straightforward exercise that we leave to the reader.
\end{proof}

@@

Then Theorem~\ref{thm:KS1} is an immediate consequence. Let us now
proceed with providing further lemmas that will be needed for the
other results.

@@

\begin{proof}
  We show that there is always a derivation
  $$
  \vlderivation{
    \vlde{\sysS}{}{A}{
      \vlhy{A \vlor A}}}
  $$, where $\sysS = \set{\acD,\me,\mfaD,\mexD,\fequ}$, by induction on $A$:
  \begin{itemize}
    \item If $A = a$, then we have
      $
      \vlderivation{
        \vlin{\acD}{}{a}{
          \vlhy{a \vlor a}}}
      $.
    \item If $A = B \vlan C$, then we have
      $
      \vlderivation{
	\vlde{\sysS}{}{B \vlan C}{
	  \vlde{\sysS}{}{B \vlan (C \vlor C)}{
	    \vlin{\me}{}{(B \vlor B) \vlan (C \vlor C)}{
	      \vlhy{(B \vlan C) \vlor (B \vlan C)}}}}}
      $.\\[.5ex]
    \item If $A = B \vlor C$, then we have
      $
      \vlderivation{
	\vlde{\sysS}{}{B \vlor C}{
	  \vlde{\sysS}{}{B \vlor (C \vlor C)}{
	    \vlin{\fequ}{}{(B \vlor B) \vlor (C \vlor C)}{
	      \vlhy{(B \vlor C) \vlor (B \vlor C)}}}}}
      $.\\[.5ex]
    \item If $A = \exists x.A'$, then we have
      $
      \vlderivation{
	\vlde{\sysS}{}{\exists x.A'}{
	  \vlin{\mexD}{}{\exists x.(A' \vlor A')}{
	    \vlhy{(\exists x.A') \vlor (\exists x.A')}}}}
      $.\\[.5ex]
    \item If $A = \forall x.A'$, then we have
      $
      \vlderivation{
	\vlde{\sysS}{}{\forall x.A'}{
	  \vlin{\mexD}{}{\forall x.(A' \vlor A')}{
	    \vlhy{(\forall x.A') \vlor (\forall x.A')}}}}
      $.
  \end{itemize}
  \todo{}
  \juihsuan{done. Maybe just keep one case.}
\end{proof}

@@

\begin{proof}
  \todo{}\lutz{also check for the need of$\fequ$}

  We have the following derivations:
  $$
  \vlderivation{
    \vlin{\cD}{}{(A \vlor B) \vlan (C \vlor D)}{
      \vlin{\wlD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan (C \vlor D))}{
	\vlin{\wlD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor ((A \vlor B) \vlan D))}{
	  \vlin{\wrD}{}{((A \vlor B) \vlan (C \vlor D)) \vlor (B \vlan D))}{
	    \vlin{\wrD}{}{((A \vlor B) \vlan C) \vlor (B \vlan D)}{
	      \vlhy{(A \vlan C) \vlor (B \vlan D)}}}}}}}
  $$.
  $$
  \vlderivation{
    \vlin{\cD}{}{\exists x.(A \vlor B)}{
      \vlin{\wlD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.(A \vlor B))}{
	\vlin{\wrD}{}{(\exists x.(A \vlor B)) \vlor (\exists x.B)}{
	  \vlhy{(\exists x.A) \vlor (\exists x.B)}}}}}
  $$.
  $$
  \vlderivation{
    \vlin{\cD}{}{\forall x.(A \vlor B)}{
      \vlin{\wlD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.(A \vlor B))}{
	\vlin{\wrD}{}{(\forall x.(A \vlor B)) \vlor (\forall x.B)}{
	  \vlhy{(\forall x.A) \vlor (\forall x.B)}}}}}
  $$.
  \juihsuan{done. If needed, we can introduce the notion of open deduction to
reduce the size of derivations...}
\end{proof}
